Data Exploration: IUCN and AquaMaps

### 2016-08-28 clip_fao/fao_clip_pac.Rmd
updated aquamaps edge map

values(rast_spp_e)[values(rast_spp_e) == 0] <- NA
values(rast_spp_e)[is.na(values(rast_spp_e))] <- 0
rast_spp_e <- crop(rast_spp_e, extent(c(85, 220, -60, 60)))

rast_spp_map_e <- 
  tm_shape(rast_spp_e) +
    tm_raster(palette = 'Reds',
              breaks = c(1, 15, 100, 200, 300, Inf),
              colorNA = 'lightblue1',
              textNA = 'Zero',
              title = 'Species count',
              alpha = 1) +
  tm_shape(World) +
    tm_polygons(border.col = 'grey50', col = 'grey55') + 
  tm_shape(fao_polys) +
    tm_borders(col = 'grey40') +
  tm_layout(basemaps = "Esri.WorldTopoMap", 
            # title.position = 'TOP', 
            legend.outside = TRUE, attr.outside = TRUE)

@@

>>>>

values(rast_spp_e)[values(rast_spp_e) == 0] <- NA
# values(rast_spp_e)[is.na(values(rast_spp_e))] <- 0
rast_spp_e <- crop(rast_spp_e, extent(c(85, 220, -59, 50)))

rast_spp_map_e <- 
  tm_shape(rast_spp_e) +
    tm_raster(palette = 'Reds',
              breaks = c(1, 15, 100, 200, 300, Inf),
              colorNA = 'lightblue1',
              textNA = 'Zero',
              title = 'Count',
              alpha = 1) +
  tm_shape(World) +
    tm_polygons(border.col = 'grey45', col = 'grey40', lwd = 0.25) + 
  tm_shape(fao_polys) +
    tm_borders(col = 'grey40', lwd = 0.25) +
    tm_text('F_CODE_1',
            col = 'orangered4',
            fontface = 'bold.italic',
            fontfamily = 'Helvetica',
            size = .35) +
  tm_layout(basemaps = "Esri.WorldTopoMap", 
            legend.text.size = .35,
            legend.title.size = .45,
            # title.position = 'TOP', 
            legend.outside = TRUE,
            # legend.position = c('right', 'bottom'),
            # legend.bg.color = 'white',
            # legend.bg.alpha = .5,
            attr.outside = TRUE)

@@

save_tmap(rast_spp_map_e, file.path(dir_fig, 'fig4_am_edge.png'), 
          width = 9, height = 6, units = 'cm', dpi = 600)
